### 2017-03-03 Objects/Objects.tex
Own final read through

\enlargethispage{\baselineskip}
Primary vertices are reconstructed by clustering
tracks that are compatible with have originated from the same vertex, then fitting 
these tracks for the position of the vertex. The clustering 
is performed using the \ac{DA} algorithm \cite{vtx-da}, which identifies
the most probable vertex candidates and assigns tracks to them. Vertex
candidates with at least two associated tracks are fitted using an adaptive
vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
vertex position. The analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} take the primary
vertex of the hard scatter to be the reconstructed vertex with the largest scalar \pT~sum of the associated
tracks. %which the scalar sum of the \pT s of
%the associated tracks is largest. %This differs from the analysis presented in chapter \ref{chap:hhh},
%where requirements on the quality of the vertex
%fit and the distance between the vertex and the nominal interaction point 
%were additionally made.
 %By doing this both the best estimate
%of the vertex position and an indicator for the success of the fit are obtained.
%Each track is assigned a weight $w_i$ between 0 and 1, where values 
%closer to 1 indicate more consistency with the vertex position.
%The number of degrees of freedom in the fit can then be defined as
%\begin{equation}\label{eqn:pv_ndof}
%n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
%\end{equation}
%which is strongly correlated with the number of tracks arising from the interaction region
%and can therefore be used to select genuine interactions. During Run 1 this variable was
%used in many analyses, including the one presented in chapter \ref{chap:hhh}, to define
%good--quality primary vertices. In addition to requiring $n_{\text{dof}}>4$, the distances
%between the vertex and the nominal interaction point were required
%to be $\Delta z< 24$ cm and $\Delta xy < 2$ cm. The primary vertex of the
%hard scatter was then taken as the vertex with greatest scalar sum \pT~ of associated
%tracks that passed these requirements. For the analyses with data from Run 2 the
%quality requirements were removed and the primary vertex of the hard scatter was simply taken
%as the reconstructed vertex with largest scalar sum \pT~ of tracks.

@@

\section{Electrons}
\label{sec:objects_ele}
Electrons are reconstructed by combining tracks from 
the inner tracker with energy deposits in the \ac{ECAL}.
A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
that will be described in section \ref{sec:objects_pf}.%FIXME don't say this, they're more similar now
Depending on the thickness of the intervening material, electrons lose up to an average of 86\% of their energy 
due to bremsstrahlung before reaching the \ac{ECAL}.
To accurately reconstruct the energy of the electron it is
important to capture the energy of the bremsstrahlung photons, which are spread in the $\phi$ direction
due to the magnetic field. To achieve this, ``supercluster'' algorithms are used.
In these algorithms the clustering
is performed by defining a seed crystal as the crystal containing a local
energy maximum above a certain threshold.
In the barrel, arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
to the cluster, stepping sideways in both directions in $\phi$ within a range
of approximately $\pm 0.3$ rad. Contiguous clusters are merged into
superclusters as long as each cluster satisfies a minimum energy deposit.
In the endcaps arrays of $5\times 5$ crystals are 
merged into superclusters within a range in $\eta$ of $\pm 0.07$ and a range in $\phi$ of $\pm 0.3$ rad.
%The array is
%only added to the cluster if the energy deposited in it is larger than a minimum.
%These clusters are grouped into superclusters if each distinct cluster has a seed array in 
%which the energy deposit is larger than a pre-defined minimum.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
and misidentified electrons at $8\,\TeV$, for data and MC]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
taken at $\sqrt{s} = 8\,\TeV$, overlaid on the distributions for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

Following this, remaining tracks lead to charged hadrons. The track is
given the momentum from the track fit, assuming the mass of a charged pion. If
the energy measured in the calorimeters is compatible with the momentum assigned
to the track, a charged hadron is identified and the
momentum redefined by fitting the tracker and calorimeter measurements. If
the energy of the calorimeter clusters linked to the track is significantly larger than the
charged particle momentum from the track fit, additional overlapping neutral particles
are identified. If the difference between the tracker momentum and the calorimeter
energy is larger than the total energy registered in associated \ac{ECAL} clusters,
a \ac{PF} photon with energy equal to the total \ac{ECAL} energy is created.
Any remaining momentum difference is assigned to a \ac{PF} neutral hadron. If the momentum
difference is smaller than the energy registered in associated \ac{ECAL} clusters 
the energy difference is only associated with a \ac{PF} photon. %Justified by fact that
%in jets 25% of the energy is carried by photons while neutral hadrons
%leave only 3% of the jet energy in the ECAL. This fraction is reduced by one order of magnitued
%for taus for which decays to final states with neutral hadrons are Cabbibo suppressed to a branching ratio of 
%about a percent.
Finally, any remaining \ac{ECAL} clusters not linked to a track give
rise to \ac{PF} photons, with any \ac{HCAL} clusters
not linked to tracks giving rise to neutral \ac{PF} hadrons.

@@

Because not all of the input variables to the \ac{CSV} algorithm are perfectly
modelled in simulation, the b-tagging efficiency for different jet
flavours is different in data and \ac{MC} simulation. Scale factors can be detemined
as the ratio of tagging efficiencies between the two, which are applied to the simulated events in order to match the data.
The measurement of the tagging efficiency
for genuine b-jets is based on samples containing a muon overlapping with the jet, 
making use of the $\approx$ 11\% semileptonic branching fraction of b-hadrons. This
measurement can be complemented by measurements from samples
with the kinematic signatures of \ttbar production, making use of 
the large $\Ptop \rightarrow \PW \Pbottom$ branching ratio. %Measurements
%of mis--tagging efficiencies for light jets are made using negative--tagging
%algorithms to select samples enriched in light jets from multijet events.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
\end{center}
\caption[\MET~distributions comparing MVA \MET~to PF \MET~for
\Zmm events, in a sample corresponding to $42\,\invpb$ of data collected
at $\sqrt{s}=13\,\TeV$.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~(black circles) for
\Zmm events, which contain no genuine \MET~, in a sample corresponding to $42\,\invpb$ of data collected at $\sqrt{s}=13\,\TeV$. The 
\MET~values for MVA \MET~are lower than for \ac{PF} \MET. (b) The \MET~resolution for \ac{PF} \MET~in blue and MVA \MET~in red/brown
circles, as a function of number of vertices. The MVA \MET~resolution is more stable with increased pileup \cite{cms-dp-mvamet}.}
\label{fig:objects_mvamet}
\end{figure}

@@

%\subsection{Isolation and discrimination against light leptons}
%\label{sec:objects_tau_iso}
Requiring the reconstructed \Pgth to be isolated reduces the jet $\rightarrow$\Pgth fake rate. Isolation
discriminators can be defined using the isolation sum,
\begin{equation}\label{eqn:cutbased_iso}
I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm}) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm}) ),
\end{equation}
where the first term denotes the sum of the transverse momenta of all charged particles not part
of the identified \Pgth. Only particles with \pT~$> 0.5\,\GeV$ within a cone of $\Delta R = 0.5$ centred around the 
direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
originated from the \Pgth production vertex within $d_z < 0.2\,\cm$. The second term denotes the sum
of the transverse momenta of photons with $\pTm > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
of the \Pgth. The effect of pileup on this term is accounted for by subtracting the sum of the momenta of charged
particles with \pT~$> 0.5\,\GeV$, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
a $\Delta \beta$ factor of 0.2.%FIXME rephrase

@@

Figure \ref{fig:tau_efficiency}a compares the \Pgth identification efficiency with the
jet$\rightarrow$\Pgth fake rate for different working points of the
MVA isolation discriminator, as well as the cut-based isolation discriminator based
on the isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA-based 
discriminator performs better than the cut-based discriminator alone.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
\subfloat[Real \Pgth efficiency for anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
\subfloat[$\Pe\rightarrow$\Pgth fake rate for the anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
\end{center}
\caption[Figures of the jet$\rightarrow$\Pgth fake rate in QCD MC events
versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same \Pgth identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real \Pgth identification
efficiency for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
the \pT~of the \Pe.}
\label{fig:tau_efficiency}
\end{figure}
The anti-muon discriminator is a cut-based discriminant, for which a loose and a tight working
point are provided. It is based on variables such as the number of track segments found in various
parts of the muon system around the direction of the \Pgth, and comparisons of calorimeter energy
with the momentum of the leading \Pgth track.
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
%Otherwise it passes the discriminator.
%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
%\end{itemize}

>>>>

\enlargethispage{\baselineskip}
Primary vertices are reconstructed by clustering
tracks that are compatible with having originated from the same vertex, then fitting 
these tracks for the position of the vertex. The clustering 
is performed using the \ac{DA} algorithm \cite{vtx-da}, which identifies
the most probable vertex candidates and assigns tracks to them. Vertex
candidates with at least two associated tracks are fitted using an adaptive
vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
vertex position. The analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} take the primary
vertex of the hard scatter to be the reconstructed vertex with the largest scalar \pT~sum of the associated
tracks. %which the scalar sum of the \pT s of
%the associated tracks is largest. %This differs from the analysis presented in chapter \ref{chap:hhh},
%where requirements on the quality of the vertex
%fit and the distance between the vertex and the nominal interaction point 
%were additionally made.
 %By doing this both the best estimate
%of the vertex position and an indicator for the success of the fit are obtained.
%Each track is assigned a weight $w_i$ between 0 and 1, where values 
%closer to 1 indicate more consistency with the vertex position.
%The number of degrees of freedom in the fit can then be defined as
%\begin{equation}\label{eqn:pv_ndof}
%n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
%\end{equation}
%which is strongly correlated with the number of tracks arising from the interaction region
%and can therefore be used to select genuine interactions. During Run 1 this variable was
%used in many analyses, including the one presented in chapter \ref{chap:hhh}, to define
%good--quality primary vertices. In addition to requiring $n_{\text{dof}}>4$, the distances
%between the vertex and the nominal interaction point were required
%to be $\Delta z< 24$ cm and $\Delta xy < 2$ cm. The primary vertex of the
%hard scatter was then taken as the vertex with greatest scalar sum \pT~ of associated
%tracks that passed these requirements. For the analyses with data from Run 2 the
%quality requirements were removed and the primary vertex of the hard scatter was simply taken
%as the reconstructed vertex with largest scalar sum \pT~ of tracks.

@@

\section{Electrons}
\label{sec:objects_ele}
Electrons are reconstructed by combining tracks from 
the inner tracker with energy deposits in the \ac{ECAL}.
A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
that will be described in section \ref{sec:objects_pf}. %FIXME don't say this, they're more similar now
Depending on the thickness of the intervening material, electrons lose up to an average of 86\% of their energy 
due to bremsstrahlung before reaching the \ac{ECAL}.
To accurately reconstruct the energy of the electron it is
important to capture the energy of the bremsstrahlung photons, which are spread in the $\phi$ direction
due to the magnetic field. To achieve this, ``supercluster'' algorithms are used.
In these algorithms the clustering
is performed by defining a seed crystal as the crystal containing a local
energy maximum above a certain threshold.
In the barrel, arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
to the cluster, stepping sideways in both directions in $\phi$ within a range
of approximately $\pm 0.3$ rad. Contiguous clusters are merged into
superclusters as long as each cluster satisfies a minimum energy deposit.
In the endcaps arrays of $5\times 5$ crystals are 
merged into superclusters within a range in $\eta$ of $\pm 0.07$ and a range in $\phi$ of $\pm 0.3$ rad.
%The array is
%only added to the cluster if the energy deposited in it is larger than a minimum.
%These clusters are grouped into superclusters if each distinct cluster has a seed array in 
%which the energy deposit is larger than a pre-defined minimum.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
and misidentified electrons at $8\,\TeV$, for data and simulation]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
taken at $\sqrt{s} = 8\,\TeV$, overlaid on the distributions for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

After this, remaining tracks lead to charged hadrons. The track is
given the momentum from the track fit, assuming the mass of a charged pion. If
the energy measured in the calorimeters is compatible with the momentum assigned
to the track, a charged hadron is identified and the
momentum redefined by fitting the tracker and calorimeter measurements. If
the energy of the calorimeter clusters linked to the track is significantly larger than the
charged particle momentum from the track fit, additional overlapping neutral particles
are identified. If the difference between the tracker momentum and the calorimeter
energy is larger than the total energy registered in associated \ac{ECAL} clusters,
a \ac{PF} photon with energy equal to the total \ac{ECAL} energy is created.
Any remaining momentum difference is assigned to a \ac{PF} neutral hadron. If the momentum
difference is smaller than the energy registered in associated \ac{ECAL} clusters 
the energy difference is only associated with a \ac{PF} photon. %Justified by fact that
%in jets 25% of the energy is carried by photons while neutral hadrons
%leave only 3% of the jet energy in the ECAL. This fraction is reduced by one order of magnitued
%for taus for which decays to final states with neutral hadrons are Cabbibo suppressed to a branching ratio of 
%about a percent.
Finally, any remaining \ac{ECAL} clusters not linked to a track give
rise to \ac{PF} photons, with any \ac{HCAL} clusters
not linked to tracks giving rise to neutral \ac{PF} hadrons.

@@

Because not all of the input variables to the \ac{CSV} algorithm are perfectly
modelled in simulation, the b-tagging efficiency for different jet
flavours is different in data and \ac{MC} simulation. Scale factors can be determined
as the ratio of tagging efficiencies between the two, which are applied to the simulated events in order to match the data.
The measurement of the tagging efficiency
for genuine b-jets is based on samples containing a muon overlapping with the jet, 
making use of the $\approx$ 11\% semileptonic branching fraction of b-hadrons. This
measurement can be complemented by measurements from samples
with the kinematic signatures of \ttbar production, making use of 
the large $\Ptop \rightarrow \PW \Pbottom$ branching ratio. %Measurements
%of mis--tagging efficiencies for light jets are made using negative--tagging
%algorithms to select samples enriched in light jets from multijet events.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
\end{center}
\caption[\MET~distributions comparing MVA \MET~to PF \MET~for
\Zmm events, in a sample corresponding to $42\,\invpb$ of data collected
at \mbox{$\sqrt{s}=13\,\TeV$}.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~(black circles) for
\Zmm events, which contain no genuine \MET~, in a sample corresponding to $42\,\invpb$ of data collected at $\sqrt{s}=13\,\TeV$. The 
\MET~values for MVA \MET~are lower than for \ac{PF} \MET. (b) The \MET~resolution for \ac{PF} \MET~in blue and MVA \MET~in red/brown
circles, as a function of number of vertices. The MVA \MET~resolution is more stable with increased pileup \cite{cms-dp-mvamet}.}
\label{fig:objects_mvamet}
\end{figure}

@@

%\subsection{Isolation and discrimination against light leptons}
%\label{sec:objects_tau_iso}
Requiring the reconstructed \Pgth to be isolated reduces the $\text{jet}\rightarrow\Pgth$ fake rate. Isolation
discriminators can be defined using the isolation sum,
\begin{equation}\label{eqn:cutbased_iso}
I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm}) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm}) ),
\end{equation}
where the first term denotes the sum of the transverse momenta of all charged particles not part
of the identified \Pgth. Only particles with \pT~$> 0.5\,\GeV$ within a cone of $\Delta R = 0.5$ centred around the 
direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
originated from the \Pgth production vertex. This is achieved by requiring the longitudinal impact parameter
with respect to the primary vertex to be $d_z < 0.2\,\cm$. The second term of equation \ref{eqn:cutbased_iso} denotes the sum
of the transverse momenta of photons with $\pTm > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
of the \Pgth. The effect of pileup on this term is accounted for by subtracting the sum of the momenta of charged
particles with \pT~$> 0.5\,\GeV$, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
a $\Delta \beta$ factor of 0.2.%FIXME rephrase

@@

Figure \ref{fig:tau_efficiency}a compares the \Pgth identification efficiency with the
$\text{jet}\rightarrow\Pgth$ fake rate for different working points of the
MVA isolation discriminator, as well as the cut-based isolation discriminator based
on the isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA-based 
discriminator performs better than the cut-based discriminator alone.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
\subfloat[Real \Pgth efficiency for anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
\subfloat[$\Pe\rightarrow$\Pgth fake rate for the anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
\end{center}
\caption[Figures of the jet$\rightarrow$\Pgth fake rate in QCD MC events
versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the \mbox{$\Pe\rightarrow\Pgth$} fake rate for different
working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same \Pgth identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real \Pgth identification
efficiency for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
the \pT~of the electron.}
\label{fig:tau_efficiency}
\end{figure}
The anti-muon discriminator is a cut-based discriminant, for which a loose and a tight working
point are provided. It is based on variables such as the number of track segments found in various
parts of the muon system around the direction of the \Pgth, and comparisons of calorimeter energy
with the momentum of the leading \Pgth track.
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
%Otherwise it passes the discriminator.
%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
%\end{itemize}
